Implicit yaddayadda

### 2011-10-28 papers/PLDI2012/implicitization.tex
typo

To prevent the algorithm from adding too many paths at a time, we
use another abstract value associated to a control point $p_j$, noted
$X_j^d$, which is distinct from $X_j^s$, and initialized to $X_j^s$.
This value is updated when a point $p_j$ is the target of a new path,
so that further SMT queries do not compute other paths with the same
source and destination if it is not needed (because these new paths
would not make $X_j^d$ grow, hence would not be returned by the SMT
solver).

@@

Guided static analysis from \citet{DBLP:conf/sas/GopanR07} yields, at line 5,
$\lstinline|x_old| \in (-\infty,+\infty)$.
Path-focusing \citep{Monniaux_Gonnord_SAS11} performs slightly
better, and finds $\lstinline|x_old| \in (-\infty,10000]$.
Now, let us see how our technique performs on this example.

@@

Our technique gives us the expected invariant 
$\lstinline|x_old| \in~[-10000,\allowbreak 10000]$. 
Here, only 3 paths out of the 25 have been computed during the analysis. In
practice, depending on the order the SMT-solver returns the paths, other
feasible paths could have been added during the analysis.

@@

Statistically, the domain of convex polyhedra gives the better results, but
regularly yields greater invariants than the domains of octagons/intervals.
Experiences shows is it mostly due to the widening operator.
The Octagon domain appears to be much better than intervals.
\JH{Commenter les resultats}

>>>>

To prevent the algorithm from adding too many path at a time, we
use another abstract value associated to a control point $p_j$, noted
$X_j^d$, which is distinct from $X_j^s$, and initialized to $X_j^s$.
This value is updated when a point $p_j$ is the target of a new path,
so that further SMT queries do not compute other paths with the same
source and destination if it is not needed (because these new paths
would not make $X_j^d$ grow, hence would not be returned by the SMT
solver).

@@

Guided static analysis from \citet{DBLP:conf/sas/GopanR07} yields at line 5
$\lstinline|x_old| \in (-\infty,+\infty)$.
Path-focusing \citep{Monniaux_Gonnord_SAS11} performs slightly
better, and finds $\lstinline|x_old| \in (-\infty,10000]$.

Now, see how our technique performs on this example.

@@

Our technique gives us the expected invariant 
$\lstinline|x_old| \in~[-10000,\allowbreak 10000]$. 
Here, only 3 paths over the 25 have been computed during the analysis. In
practice, depending on the order the SMT-solver returns the paths, other
feasible paths could have been added during the analysis.

@@

Statistically, the domain of convex polyhedra gives the better results, but
regularly yields greater invariants than the domains of octagons/intervals.
Experiences shows it is mostly due to the widening operator.
The Octagon domain appears to be much better than intervals.
\JH{Commenter les resultats}
